Arbitrary Precision and Arbitrary $n$-grams

### 2011-02-28 paper/paper.Rnw
"problematic"

	Our design is built around dictionaries for each n-gram we consider.  We
	break the input text into words and add sentence separators (although we do
	not break the sentences apart, so trigrams or higher can cross sentence
	boundaries), and then process the list of words, tallying the number of each
	$n$-gram seen in the dictionary.

@@

	Each subsection contains two examples from the Shakespeare corpus and two
	from War and Peace.  These corpora were chosen because they were determined
	at rough glance to be the easiest to parse and had the fewest problematic.

@@

\begin{figure}
\begin{center}
<<echo=F,fig=T>>=
#pp_gen.plot(results.shakespeare,'Shakespeare')
@
\end{center}
\end{figure}

>>>>

	Our design is built around dictionaries for each $n$-gram we consider.  We
	break the input text into words and add sentence separators (although we do
	not break the sentences apart, so trigrams or higher can cross sentence
	boundaries), and then process the list of words, tallying the number of each
	$n$-gram seen in the dictionary.

@@

	Each subsection contains two examples from the Shakespeare corpus and two
	from War and Peace.  These corpora were chosen because they were determined
	at rough glance to be the easiest to parse. %and had the fewest problematic.

@@
